A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-14 EvoPar2017/paper.Rnw
Adds entropy and references

This is interesting in the sense that in indicates that there might be
something more to performance that just the number of volunteers
contributing.
%
\begin{figure}[ht!b]
\centering
<<entropy, cache=FALSE,echo=FALSE>>=
max <- max(new.experiment.data$IPs)
exp.palette <- colorRampPalette(brewer.pal(12,"Paired"))
ggplot(data=new.experiment.data)+geom_point(aes(x=entropy,y=milliseconds,size=PUTs,color=IPs))+scale_x_log10()+scale_y_log10()+scale_color_gradient(limits=c(1,max),low='red')
@ %def entropy data
%
\caption{Entropy of the user contribution vs. time to solution in the
  volunteer computing experiment. \label{fig:entropy}}
\end{figure}

>>>>

This is interesting in the sense that in indicates that there might be
something more to performance that just the number of volunteers
contributing. In this experiment we include an additional measure:
user-contribution entropy, which is measure by computing the
compression entropy of the user contributions every for the whole
experiment.  This is computed converting the sequence of the number of
PUTs into a string and then compressing it using {\tt Zlib}, a
standard compression library. Since the compression rate is related to
the randomness of the sequence, a higher compression rate will
correspond to an experiment with a low entropy, while a lower
compression rate will indicate that there has been a certain amount of
unexpected changes during the experiment. Although less popular than
Jenssen-Shannon entropy, this way of measuring it is widely used
\cite{ornstein1993entropy} in case where we want to compute the
entropy of sequences of events, such as arrhythmias
\cite{baumert2004forecasting}. Unlike Jenssen-Shannon entropy, the
range of the compression entropy will vary between 0 (lower, or worse
compression rate) and 1 (no compression). 
%
\begin{figure}[ht!b]
\centering
<<entropy, cache=FALSE,echo=FALSE>>=
max <- max(new.experiment.data$IPs)
exp.palette <- colorRampPalette(brewer.pal(12,"Paired"))
ggplot(data=new.experiment.data)+geom_point(aes(x=entropy,y=milliseconds,size=PUTs,color=IPs))+scale_x_log10()+scale_y_log10()+scale_color_gradient(limits=c(1,max),low='red')
@ %def entropy data
%
\caption{Entropy of the user contribution vs. time to solution in the
  volunteer computing experiment. \label{fig:entropy}}
\end{figure}

### 2016-11-14 EvoPar2017/paper.tex
Adds entropy and references

This is interesting in the sense that in indicates that there might be
something more to performance that just the number of volunteers
contributing.
%
\begin{figure}[ht!b]
\centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/entropy-1}

>>>>

This is interesting in the sense that in indicates that there might be
something more to performance that just the number of volunteers
contributing. In this experiment we include an additional measure:
user-contribution entropy, which is measure by computing the
compression entropy of the user contributions every for the whole
experiment.  This is computed converting the sequence of the number of
PUTs into a string and then compressing it using {\tt Zlib}, a
standard compression library. Since the compression rate is related to
the randomness of the sequence, a higher compression rate will
correspond to an experiment with a low entropy, while a lower
compression rate will indicate that there has been a certain amount of
unexpected changes during the experiment. Although less popular than
Jenssen-Shannon entropy, this way of measuring it is widely used
\cite{ornstein1993entropy} in case where we want to compute the
entropy of sequences of events, such as arrhythmias
\cite{baumert2004forecasting}. Unlike Jenssen-Shannon entropy, the
range of the compression entropy will vary between 0 (lower, or worse
compression rate) and 1 (no compression). 
%
\begin{figure}[ht!b]
\centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/entropy-1}
